Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-13 paperIEEE.tex
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@126 db7c848b-7755-4df2-b763-8796797afa52

For sort-first and sort-last rendering we present static and load-balanced task
decomposition. For readability, we only present the results of the equalizer
(load or tree) providing the better performance for each application.
Unsurprisingly, static decompositions perform worse over load-balanced
compounds. Sort-first polygon rendering exhibits oscillations in performance as
nodes are added to the task, due to unfavorable assignment of a tile with a high
work load on odd node counts. Static sort-last volume rendering has a similar
oscillation behaviour \FIXME{due to @David?}.

The simpler \textsf{tree\_equalizer} outperforms in almost all cases the
load-grid-driven \textsf{load\_equalizer}, except for sort-first volume
rendering where the load in the region of interest is relatively uniform. This
counterintuitive result seems to again confirm that simple algorithms often
outperform theoretically better, but more complex implementations. On the other
hand, the \textsf{tile\_equalizer} often outperforms \textsf{tree\_equalizer}.
This suggests that the underlying implicit load balancing can be superior to the
explicit methods of \textsf{load\_equalizer} and \textsf{tree\_equalizer} in
high load situations, where the additional overhead of tile generation and
distribution is more justified. The relative simple nature of our benchmark
application's rendering algorithms is also favoring work packages, since it has
a near-zero static overhead per rendering pass.

>>>>

For sort-first and sort-last rendering we present static and load-balanced task
decomposition. For readability, we only present the results of the equalizer
(load or tree) providing the better performance for each application.
Unsurprisingly, static decompositions perform worse over load-balanced
compounds. Sort-first polygon rendering exhibits oscillations in performance as
nodes are added to the task, due to unfavorable assignment of a tile with a high
work load on odd node counts. Static sort-last volume rendering has a similar
oscillation behaviour, as ranges of scene geometry tend to also get unfavorably assigned under such conditions.

The simpler \textsf{tree\_equalizer} outperforms in almost all cases the
load-grid-driven \textsf{load\_equalizer}, except for sort-first volume
rendering where the load in the region of interest is relatively uniform. This
counterintuitive result seems to again confirm that simple algorithms often
outperform theoretically better, but more complex implementations. On the other
hand, the \textsf{tile\_equalizer} often outperforms \textsf{tree\_equalizer}.
This suggests that the underlying implicit load balancing can be superior to the
explicit methods of \textsf{load\_equalizer} and \textsf{tree\_equalizer} in
high load situations, where the additional overhead of tile generation and
distribution is more justified. The relatively simple nature of our benchmark
application's rendering algorithms is also favoring work packages, since it has
a near-zero static overhead per rendering pass.
